\documentclass[12pt]{letter}
\usepackage{graphicx}
\usepackage[letterpaper,top=2.54cm,bottom=2.54cm,left=2.54cm,right=2.54cm]{geometry}
\usepackage{mathptmx} %times-new-roman

\begin{document}
I have chosen courses in my program to build a strong foundation in reactor
physics, advanced numerical methods, and high-performance computing (HPC),
equipping me with the necessary skills to develop efficient, scalable
algorithms for deterministic neutron transport and model the highly coupled
physics of advanced reactors.

NPRE 555 will give me hands-on experience with neutron transport solvers,
helping identify methods suited for optimization and parallelization. NPRE 560,
focused on reactor kinetics, is crucial for modeling time-dependent phenomena
in advanced reactors, ensuring accurate simulations of advanced reactors.

CS 483 introduces parallel programming, such as how to map computations to
parallel hardware. CS 484 builds on this by exploring parallelization
frameworks like OpenMP and MPI, vital for HPC applications. Together, these
courses will help me design efficient parallel solutions for computationally
intensive problems inherent to deterministic neutron transport.

CS 555 and CS 556 provide a strong foundation in numerical methods for solving
PDEs and linear systems. CS 555 introduces the Finite Element Method (FEM), a
method widely used in computational nuclear engineering. These courses will
provide the numerical methods foundation necessary for accurate solutions.  

CS 554 focuses on parallelizing numerical algorithms for HPC systems. This
course will build on my understanding of linear systems from CS 556 and
parallel computing from ECE 408/CS 483. While not specific to GPUs, it will
grant insights into designing efficient parallel solvers, necessary for
deterministic neutron transport codes.

ECE 508 will introduce me to critical optimization techniques such as problem
decomposition and memory management. These are essential for adapting
deterministic neutron transport to GPUs, as such methods are typically
memory-intensive and GPUs have limited memory resources compared to CPUs.

These courses will provide the technical foundation necessary to address the
complexities of neutron transport simulations and reactor modeling. I will be
equipped to develop efficient and scalable computational tools for
next-generation reactors.
\end{document}

%POS:
% * Science and Engineering: NPRE 555/560
% * Computer Science and Engineering: 483/484 (508***)
% * Applied Mathematics and Statistics: CS 556/555
% * High-Performance Computing: CS 554
