\documentclass[12pt]{letter}
\usepackage{graphicx}
\usepackage[letterpaper,top=2.54cm,bottom=2.54cm,left=2.54cm,right=2.54cm]{geometry}
\usepackage{mathptmx} %times-new-roman

\begin{document}
As part of my research with the Multiphysics and Multiscale Simulations
research group at the University of Illinois Urbana-Champaign, I investigated
the applicability of Functional Expansion Tallies (FETs) to complex,
non-homogeneous reactor geometries using OpenMC, a Monte Carlo neutron
transport code. The most complex geometry I studied was a TRistructural
ISOtropic fuel (TRISO) particle compact --- a small hexagonal graphite block
containing tens of thousands of TRISO particles. The simulation involved
500,000 particles, 1,000 batches (500 inactive and 500 active), and a 200th
order Zernike FET (20,101 polynomials). This FET tallied kappa-fission, the
recoverable energy production rate due to fission. The problem ran on 4 CPU
cores with a wall time of approximately four hours. The results revealed that
even a 200th order Zernike FET failed to accurately approximate the radial and
angular power distribution due to steep power gradients at material interfaces.
This highlighted the challenge of applying FETs to problems with complex,
non-homogenous geometries.

With computational resources 100 times more powerful, I could expand the
Zernike FET to a much higher radial order, potentially capturing the steep
gradients more effectively. Alternatively, I could model an entire array of
hexagonal compacts, and apply the Zernike FET over all of the compacts. This
would potentially result in a better approximation of the mean power
distribution by reducing the relative impact of hyper-local dependencies.
However, expanding from a single compact to a full array introduces
mathematical challenges. The Zernike family is orthogonal over a unit disc,
perfectly aligning with the cylindrical center of a single compact, the portion
of the compact that is filled with TRISO particles. A full array would no
longer conform to this geometry and would require a sophisticated mapping of
the unit disc to an irregular polygon. This mapping is not yet available in
OpenMC, presenting a significant mathematical hurdle that would need to be
addressed to fully leverage the increased computational power. 
\end{document}
